TCP Rax: Deep Reinforcement Learning for TCP Congestion Control

### 2018-01-31 tex/petri_net.tex
Update tex and bib tex

  \begin{scope}
    \node [place,tokens=1] (s1) at (0, 1) [label={[align=center]left:Receive\\ feedback}] {};
    \node [place] (s2) at (1, 2) [label={[align=center]above:Received\\ ACK}] {};
    \node [place] (s3) at (2, 1) [label={[align=center]right:Packets\\ in the\\ network}] {};
    \node [place] (s4) at (1, 0) [label={[align=center]below:Open congestion\\ window (cwnd)}] {};

@@

    \node [transition] (e5) at (0, 2) [label={[align=center]left:Received\\ feedback}] {}
      edge [pre] node {1} (s2)
      edge [post] node {1} (s1);

>>>>

  \begin{scope}
    \node [place,tokens=1] (s1) at (0, 1) [label={[align=center]left:Received\\ feedback}] {};
    \node [place] (s2) at (1, 2) [label={[align=center]above:Received\\ ACKs}] {};
    \node [place] (s3) at (2, 1) [label={[align=center]right:Packets\\ in the\\ network}] {};
    \node [place] (s4) at (1, 0) [label={[align=center]below:Open congestion\\ window (cwnd)}] {};

@@

    \node [transition] (e5) at (0, 2) [label={[align=center]left:Receive\\ feedback}] {}
      edge [pre] node {1} (s2)
      edge [post] node {1} (s1);
